Learning by Teaching a Robot: the Case of Handwriting

### 2015-07-02 main.tex
List of studies

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Field Applications}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Studies at School}

\begin{figure}
    \centering
    \includegraphics[height=3.9cm]{schools}
    \includegraphics[height=3.9cm]{schools2}
    \caption{The first field studies were focused on technical validation, with
    above 100 pupils interacting with the robot over short periods (around 20
minutes), either alone or in small groups.}
    \label{fig:schools}
\end{figure}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Case Study 1: Diego}

\subsection{Context, Study Design}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Interaction Design}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Field Studies}

To date, the presented system has been deployed and tested in three different
schools (totalling child-robot interactions with more than 70 children, aged 5
to 8) and we also conducted 2 case studies over several weeks.
Table~\ref{studies} gives an overview of these studies.

\begin{table}[ht!]
\centering
\caption{Field studies conducted within the project}
\label{studies}
\begin{tabular}{@{}lp{4.5cm}p{2.2cm}p{2.5cm}l@{}}
\toprule
{\bf Study}     & {\bf Type}                                    & {\bf Duration}              & {\bf Children \#}                     & {\bf Ages} \\ \midrule
{\it ISG 1}     & Unstructured group interaction at school      & 16 min/group               & 4 $\times$ 8 children                 & 6-7        \\
{\it Florimont} & Individual/Pair interaction at school         & 11 min/group               & 7 (individual) + 7 $\times$ 2 (pairs) & 7-8        \\
{\it Diego}     & Case-study, spanning over 4 weeks              & 1.5 hours $\times$ 4 weeks & 1                                     & 5          \\
{\it Haut-Lac}  & Pair (with turn-taking) interaction at school & 26 min/group                            & 7 $\times$ 2                          & 5-6        \\
{\it ISG 2}     & Individual interaction at school              & 18 min                            & 6                                     & 5-6        \\
{\it Henry}     & Case-study, spanning over 4 weeks              & 1h $\times$ 4 weeks        & 1                                     & 5          \\ \bottomrule
\end{tabular}
\end{table}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Studies at School}

\begin{figure}
    \centering
    \includegraphics[height=3.9cm]{schools}
    \includegraphics[height=3.9cm]{schools2}
    \caption{The first field studies were focused on technical validation, with
    above 70 pupils interacting with the robot over short periods (around 15
minutes), either alone or in small groups.}
    \label{fig:schools}
\end{figure}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Case Study 1: Diego}
